### 2015-07-08 2015-compmorphon-morphver/poster.tex
development cycle
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61214 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{tikz}
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			%(1) look at frequency list --> check word --> if it's missing stem, add --> (1) ; if it's bad phonology --> fix phonology --> (1)
			\begin{tikzpicture}[node distance = 2cm, auto]
				% Place nodes
				\node [block] (init) {analyse corpus};
				\node [cloud, left of=init] (addstem) {add stem};
				\node [cloud, right of=init] (fixphon) {fix phonology};
				\node [block, below of=init] (freq) {examine frequency list};
				%\node [block, below of=identify] (evaluate) {evaluate candidate models};
				%\node [block, left of=evaluate, node distance=3cm] (update) {update model};
				\node [decision, below of=freq] (decide) {cause for unanalysed forms?};
				%\node [block, below of=decide, node distance=3cm] (stop) {stop};
				% Draw edges
				\path [line] (init) -- (freq);
				\path [line] (freq) -- (decide);
				\path [line] (decide) -| node [near start] {missing stem} (addstem);
				\path [line] (decide.east) -| node [near start] {bad phonology} (fixphon);
				\path [line,dashed] (addstem) -- (init);
				\path [line,dashed] (fixphon) -- (init);
			\end{tikzpicture}
		}
